partial: An R Package for Creating Partial Dependence Plots

### 2016-08-09 manuscript/greenwell.tex
minor edits

To illustrate, consider Edgar Anderson's iris data from the \pkg{datasets} package. The \code{iris} data frame contains the sepal length, sepal width, petal length, and petal width (in centimeters) for 50 flowers from each of three species of iris:  setosa, versicolor, and virginica. We fit a support vector machine with a radial basis function kernel to the data usinv the \code{svm} function in the \pkg{e1071} (the model parameters were determined using 5-fold cross-validation).
\begin{example}
library(e1071)
iris.svm <- svm(Species ~ ., data = iris, kernel = "radial", gamma = 0.75,
                cost = 0.25, probability = TRUE)
\end{example}
The \code{partial} function has to be able to extract the predicted probabilities for each class, so it is necessary to invoke the \code{prob.model = TRUE} option in the call to \code{svm}.

>>>>

To illustrate, consider Edgar Anderson's iris data from the \pkg{datasets} package. The \code{iris} data frame contains the sepal length, sepal width, petal length, and petal width (in centimeters) for 50 flowers from each of three species of iris:  setosa, versicolor, and virginica. We fit a support vector machine with a radial basis function kernel to the data using the \code{svm} function in the \pkg{e1071} (the model parameters were determined using 5-fold cross-validation).
\begin{example}
library(e1071)
iris.svm <- svm(Species ~ ., data = iris, kernel = "radial", gamma = 0.75,
                cost = 0.25, probability = TRUE)
\end{example}
The \code{partial} function has to be able to extract the predicted probabilities for each class, so it is necessary to invoke the \code{prob.model = TRUE} option in the call to \code{svm}.
